A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-07-04 idetc2018_journal.tex
minor typos

The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
In the majority of the methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.

@@

Let's see an example of this in a motion generation task.
The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
For this type of problem, only finite solutions exist and in this case only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together.
This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.

@@

The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
we employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for a parametric path and motion.
A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

The original contributions in the paper are as follows:
1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach,
%The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis of open prescribed tasks.

@@

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
Where, $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].

@@

\begin{eqnarray}\label{nnlayer}
  h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
  ReLU(x) = max(0, x),
\end{eqnarray}
where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
Auto-encoders are trained to reconstruct the input.
In this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
The objective of training is to find out the set of weights and biases that minimizes the error loss given by,

@@

The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
The task can also be treated as a finite position motion generation and solved for valid solutions.
We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
Although, the prescribed motion entails this information, precision point approach cannot capture it.

Now we employ the approach presented in this paper.
The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
Next, we raise the signature query for nearest signatures among cluster centers of the database.
Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
Coupler motions of these linkages have a part, which matches with the shape of input motion query.
Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
All of these linkages satisfactorily perform the input task without any defect.
As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
Although Fig.~\ref{ex2_solns} shows that $5^{th}$ and $7^{th}$ solution may slightly interfere with the ground, it can be rectified by lifting the mechanism slightly up or making small changes in coupler dimensions.
In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.

@@

Although the partial matching metric is more accurate, it is expensive in terms of computation cost.
Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering of the database.
The problem formulation is invariant with respect to translation, orientation, and scaling.
Hence, constraints like geometric restrictions on pivots have to be addressed after finding feasible solutions for the task.
The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
However, the database size increases exponentially with the number of links in the mechanisms.
As an example, a Watt type six-bar database needs to be roughly 400 times larger than four-bar database.
A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.
Overall, the method provides a holistic approach towards the prescribed path and motion synthesis and encourages artificial intelligence techniques to make an impact.

>>>>

The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
In the majority of methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.

@@

Let's see an example of this in a motion generation task.
The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together.
This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.

@@

The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
we employ pattern recognition and computational shape analysis to create an invariant signature for the prescribed path and motion.
A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

The original contributions in the paper are as follows:
1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach,
%The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis.

@@

Consider a motion given in parametric form as, $x:x(t), y:y(t), \theta:\theta(t)$.
Where $\theta(t)$ is the change in orientation along the path with respect to initial orientation.
It should be noted that $\theta(t)$ is a continuous curve with domain ($-\infty$, $\infty$) in contrast to conventional domain i.e. [$-\pi$, $\pi$].

@@

\begin{eqnarray}\label{nnlayer}
  h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
  ReLU(x) = max(0, x),
\end{eqnarray}
where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
Auto-encoders are trained to reconstruct the input.
In this way, each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
The objective of training is to find out the set of weights and biases that minimizes the error loss given by,

@@

The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
The task can also be treated as a finite position motion generation and solved for valid solutions.
We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
Although the prescribed motion entails this information, precision point approach cannot capture it.

Now we employ the approach presented in this paper.
The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
Next, we raise the signature query for nearest signatures among cluster centers of the database.
Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
Coupler motions of these linkages have a part, which matches with the shape of input motion query.
Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
All of these linkages satisfactorily perform the input task without any defect.
As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
Although Fig.~\ref{ex2_solns} shows that $5^{th}$ and $7^{th}$ solution may slightly interfere with the ground, it can be rectified by lifting the mechanism slightly up or making small changes in coupler dimensions.
In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.

@@

Although the partial matching metric is more accurate, it is expensive in terms of computation cost.
Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering of the database.
The problem formulation is invariant with respect to translation, orientation, and scaling.
Hence, constraints like geometric restrictions on pivots have to be addressed after finding feasible solutions for the task.
The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
However, the database size increases exponentially with the number of links in the mechanisms.
As an example, a Watt type six-bar database needs to be roughly 400 times larger than the four-bar database.
A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.
Overall, the method provides a holistic approach towards the prescribed path and motion synthesis and encourages artificial intelligence techniques to make an impact.
